### 2015-01-26 p3/submission.Rmd
small update + update html
add breaks to keep lines under 80 characters

```{r echo=FALSE, message=FALSE}
df$rating <- ifelse(df$quality < 5, 'bad', ifelse(df$quality < 7, 'average', 'good'))
df$rating <- ordered(df$rating, levels = c('bad', 'average', 'good'))
summary(df$rating)
```

@@

From these plots, it appears that chlorides and sulphates have a small number of high outliers.

>>>>

```{r echo=FALSE, message=FALSE}
df$rating <- ifelse(df$quality < 5, 'bad', ifelse(
  df$quality < 7, 'average', 'good'))
df$rating <- ordered(df$rating,
                     levels = c('bad', 'average', 'good'))
summary(df$rating)
```

@@
